\chapter{Introduction}
The product that we want to deliver to our customers described in this paper is
a simple console application. This application is intended to be used
both from customers and owners of restaurants. The first will use this
application to
reserve a table, choosing from a list of restaurants, the latters will be able to
make their restaurants known from a larger amount of people, in an easy way.
Moreover restaurant's owners will be able to provide a description of their
restaurant, the number of seats available, which type of food can be found, where
are located, when they are open, and a telephone number.
Customers instead will be able to search a restaurant specifying their
preferences on the food and the location, after that they have choose they will 
be able to reserve the number of desired seats, specifying  date, hour, and if 
they want, add some notes for the owner, for example if there are some people 
that need a particular variation to the menu, because of some health problem or a
special diet. The application will alse manage the case in which a customer need
to cancel his/her reservation or modify it (add/remove some seats, if there are
available).
The application will handle all the reservation process, in order to make it
easier and faster both for customers and owners. The application should be
available for the largest number of users possible in order to have a large
scale and easy spreading among them, moreover should be easy to use and everyday
available.
